Tweets

### 2020-05-15 Rmd/tweets.Rmd
updated tweets collection

1. Write a R script to query twitter streaming api to get 1 percent sample over 5'.
1. Demonstrate how to set up a crontab to execute script every 5'.
1. Verify that crontab approach works by running it on my computer for, say, 15'.
    1. Cautions about twitter databases: deletions and amendments to tweets
1. Examine structure of JSON obtained from api. 
1. Create phony JSON to represent a collection of tweets.
    1. Use lorem ipsum for text of tweets

@@

```{r}
rtweet::stream_tweets(
  timeout = (15),
  parse = FALSE,
  file_name = paste0("../data/", lubridate::now(), "-tweets")
)
```

@@

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 10:36:09-tweets.json", verbose = TRUE) %>%
  dplyr::filter(lang == "en") %>%
  tidytext::unnest_tokens(output = word, input = text)
```

@@

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
```

```{r}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
library(tidytext)
word_counts <- tweets %>% 
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```

@@

```{r}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 8)
```

>>>>

1. Write a R script to query twitter streaming api to get 1 percent sample over 5'.
1. Demonstrate how to set up a crontab to execute script every 5'.
1. Verify that crontab approach works by running it on my computer for, say, 15'.
    1. Cautions about twitter databases: deletions and amendments to tweets
1. Examine structure of JSON obtained from api.

@@

@@

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) %>%
  dplyr::mutate(status_id = as.character(status_id))
```

## Dehydrate tweets for sharing

```{r}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = format(status_id, scientific = FALSE))
readr::write_csv(tibble::tibble(status_id = c(tweets$status_id, broken_ids$status_id)), col_names = FALSE, path = "../data/2020-05-10-status-ids.csv")
```

## Rehydrate tweets by querying Twitter

```{r}
# need multiple calls to get all tweets rehydrated
tweets_rehydrated <- rtweet::lookup_tweets(statuses = tweets$status_id, parse = TRUE)
```

@@

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
remove_reg <- "&amp;|&lt;|&gt;"
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

```{r}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
# https://www.tidytextmining.com/twitter.html
word_counts <- tweets_rehydrated %>% 
  dplyr::filter(lang == "en") %>%
  dplyr::filter(!stringr::str_detect(text, "^RT")) %>%
  dplyr::mutate(text = stringr::str_remove_all(text, remove_reg)) %>%
  tidytext::unnest_tokens(output = word, input = text) %>%
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```

@@

```{r}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 15)
```
